Analysis : exp220 - 228 (Nov 2018, for J Neurophys draft 2018)

### 2019-05-08 resistingrhythm/analysis/paper_figures_v4.Rmd
Limited osc_rate: 0-3 (from 0-6)

# Load all data
```{r, message=FALSE}
# -----------------------------------------------------------------------
# 16: Burst E, with H
exp_code <- 224
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4) # 4

@@

# -----------------------------------------------------------------------
# 15: Sustained E, with H
exp_code <- 221
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

@@

# -----------------------------------------------------------------------
# 22: Sustained E, with NO H
exp_code <- 220
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

@@

# -----------------------------------------------------------------------
# 21: Sustained I, with H
exp_code <- 223
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

@@

# -----------------------------------------------------------------------
# 23: Sustained I, with NO H
exp_code <- 222
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

@@

# -----------------------------------------------------------------------
# 30: Burst I, with H
# HERE
exp_code <- 227
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

@@

# -----------------------------------------------------------------------
# Calcium exp, E, sustained
exp_code <- 228
osc_codes <- c(105, 115, 125, 135, 145, 155)
osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
stim_codes <- c(3)

@@

# -----------------------------------------------------------------------
# # Add default Ca value, from exp
exp_code <- 221
osc_codes <- c(105, 115, 125, 135, 145, 155)
osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
stim_codes <- c(3)
ca_targets <- c(0.003, 0.003, 0.003, 0.003)

@@

# Figure: Error
```{r, fig.width=3.2, fig.height=1.2}
# ------------------------------------------------------------
# Kappa
results220 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(mse_error), SD_error=sd(mse_error), 
    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
tmp1$mode <- rep("No homeostatsis", nrow(tmp1))
results221 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(mse_error), SD_error=sd(mse_error), 
    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp2
tmp2$mode <- rep("Homeostatsis", nrow(tmp2))

# Kappa
bind_rows(tmp1, tmp2) %>% 
ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
  geom_point(size=1.25) +
  geom_errorbar(mapping=aes(x=M_kappa, ymin=M_error - SD_error, ymax=M_error + SD_error),
                width=0.004, size=0.2) +
  geom_errorbarh(mapping=aes(y=M_error, xmin=M_kappa - SD_kappa, xmax=M_kappa + SD_kappa),
                 height=0.002, size=0.2) +
  scale_color_manual(values=c("black", "darkgrey")) +
  labs(title="a.", y="Log error (s)", x="Kappa") +
  lims(x=c(0.0, 0.25)) +
  scale_y_log10() + annotation_logticks() +
  theme_classic2() + 
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.position = "none") -> p1

# Rate
# bind_rows(tmp1, tmp2) %>% 
# ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
#   geom_point(size=0.2) +
#   geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
#                 width=0.004, size=0.2) +
#   geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
#                  height=0.002, size=0.2) +
#   scale_color_manual(values=c("black", "darkgrey")) +
#   labs(title="c.", y="Log error (s)", x="Pop. rate") +
#   # lims(x=c(0.0, 0.25)) +
#   scale_y_log10() + annotation_logticks() +
#   theme_classic2() + 
#   theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
#         legend.position = "none") -> p3

# ---------------------------------------------------------------------
results220 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
      M_error=mean(mse_error), SD_error=sd(mse_error), 
      M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
      M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
tmp1$mode <- rep("No homeostatsis", nrow(tmp1))
results224 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(mse_error), SD_error=sd(mse_error), 
    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp2
tmp2$mode <- rep("Homeostatsis", nrow(tmp2))

# Kappa
bind_rows(tmp1, tmp2) %>% 
ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
  geom_point(size=1.25) +
  geom_errorbar(mapping=aes(x=M_kappa, ymin=M_error - SD_error, ymax=M_error + SD_error),
                width=0.004, size=0.2) +
  geom_errorbarh(mapping=aes(y=M_error, xmin=M_kappa - SD_kappa, xmax=M_kappa + SD_kappa),
                 height=0.002, size=0.2) +
  scale_color_manual(values=c("black", "darkgrey")) +
  labs(title="b.", y="Log error (s)", x="Kappa") +
  lims(x=c(0.0, 0.25)) + annotation_logticks() +
  theme_classic2() + 
  scale_y_log10() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.title=element_blank()) -> p2

# Rate
# bind_rows(tmp1, tmp2) %>% 
# ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
#   geom_point(size=0.2) +
#   geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
#                 width=0.004, size=0.2) +
#   geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
#                  height=0.002, size=0.2) +
#   scale_color_manual(values=c("black", "darkgrey")) +
#   labs(title="d.", y="Log error (s)", x="Pop. rate") +
#   # lims(x=c(0.0, 0.25)) +
#   theme_classic2() + 
#   scale_y_log10() +
#   theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
#         legend.title=element_blank()) -> p4

# -
p5 <- textGrob("Tonic")
p6 <- textGrob("Burst", gp=gpar(col="darkgoldenrod3"))

# -
layout_matrix <- rbind(
  c(3, 3, 3, 4, 4, 4, 4, NA),
  c(1, 1, 1, 2, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2, 2)
)
grid.arrange(p1, p2, p5, p6, layout_matrix=layout_matrix)

png(file="fig3.png", bg="white", width=6.4, height=2.4, unit="in", res=300)
grid.arrange(p1, p2, p5, p6, layout_matrix=layout_matrix)
dev.off()
```

>>>>

# Load all data
```{r, message=FALSE}
# -----------------------------------------------------------------------
# 16: Burst E, with H
exp_code <- 224
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4) # 4

@@

# -----------------------------------------------------------------------
# 15: Sustained E, with H
exp_code <- 221
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

@@

# -----------------------------------------------------------------------
# 22: Sustained E, with NO H
exp_code <- 220
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

@@

# -----------------------------------------------------------------------
# 21: Sustained I, with H
exp_code <- 223
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

@@

# -----------------------------------------------------------------------
# 23: Sustained I, with NO H
exp_code <- 222
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

@@

# -----------------------------------------------------------------------
# 30: Burst I, with H
# HERE
exp_code <- 227
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

@@

# -----------------------------------------------------------------------
# Calcium exp, E, sustained
exp_code <- 228
osc_codes <- c(105, 115, 125)
osc_rates <- c(0.5, 1.5, 2.5)
stim_codes <- c(3)

@@

# -----------------------------------------------------------------------
# # Add default Ca value, from exp
exp_code <- 221
osc_codes <- c(105, 115, 125)
osc_rates <- c(0.5, 1.5, 2.5)
stim_codes <- c(3)
ca_targets <- c(0.003, 0.003, 0.003, 0.003)

@@
